The influence of massive early merger events on the chemo-dynamics of galaxy discs

### 2022-10-18 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
    \begin{centering}
        \includegraphics[width=\linewidth]{static/279e12_merger_ratio_gas.pdf}
        \caption{

        }
        \label{fig:merger_ratio}
    \end{centering}
\end{figure}

>>>>

\begin{figure}
    \script{gas_profile.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/2.79e12_gas_profile_2d.pdf}
        \caption{
            Surface density profile of the cold gas before and after the two merger events. Outside of a radius of 5 kpc the merging satellites contribute cold gas up to a factor of 4 in surface density.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure}

\begin{figure*}
    \script{feh_gradient.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/feh_gradient.pdf}
        \caption{
            Metallicity gradient of the cold gas disk during the merger events. We find that the contribution of additional metal poor gas lowers the metallicity in the outskirts of the disk effectively steepening the metallicity gradient by $\sim 0.1$ dex.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure*}

\begin{figure}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/279e12_merger_ratio_gas.pdf}
        \caption{
        }
        \label{fig:merger_ratio}
    \end{centering}
\end{figure}
